---
title: "Chain pharmacies analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{chain-pharmacies-analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


This is the methodology behind a lot of the numbers that ended up in our [article](https://www.washingtonpost.com/investigations/2019/11/07/height-crisis-walgreens-handled-nearly-one-five-most-addictive-opioids/) on Walgreens. There are thirteen big numbers in the narrative of the story.

First, let's load up the packages we need.

There's a lot of new ones listed here so we can make fancy tables.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# Uncomment and run the lines below to see if you have the packages required already installed
# packages <- c("dplyr", "ggplot2", "jsonlite", "knitr", "geofacet", "scales")
# if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
#   install.packages(setdiff(packages, rownames(installed.packages())), repos = "http://cran.us.r-project.org") # }

library(arcos)
library(dplyr)
library(ggplot2)
library(lubridate)
library(data.table)
library(formattable)
library(stringr)
library(scales)
library(knitr)
```

### 1. Walgreens purchased nearly one out of every five oxycodone and hydrocodone pills

```{r 1}

```

```{r
### FACTS ----
# 1. Walgreens purchased nearly one out of every five oxycodone and hydrocodone pills
# 2. Walgreens bought 13 billion pills from 2006 - 2012
# 3. Walgreens obtained 97 percent of its pain pills from itself
# 4. Total pharmacies, around 8,000 in 2012
# 5. Walgreens ordered 31 percent more oxycodone and hydrocodone pills per store on average compared to CVS pharmacies and 73 percent more compared to the rest worldwide
# 6. Oviedo store: 30 milligram oxycodone pills doubled from 72,900 in March 2011 to 145,300 pills in July 2011
# 7. Walgreens pharmacy on McHenry Avenue was the single largest purchaser of pain pills in the entire Walgreens chain from 2006 through 2012
# 8. About one out of every five oxycodone pills ordered at the Modesto pharm was 30 milligrams.
# 9. Walgreens and four other national chain pharmacies purchased about 1.6 billion of those pills, or roughly one-third of all distributed from 2006 through 2012. 
# 10. ### At walgreens, those pills accounted for about 6 percent of the chain's overall opioid business compared to roughly 4.6 percent at CVS and 2 percent at walmart
# 11. The Greenville store was the largest buyer of pain pills in the county from 2006 through 2012, and half of the pills ordered were oxycodone-- nearly twice the average of all other pharmacies nationwide
# 12. By the end of 2012, orders of pain pills dipped to 2.2 billion from its peak of 2.4 billion the previous year, analysis shows.
# 13. But Walgreens was still the largest buyer of pills containing oxycodone and hydrocodone

### Setting up ----

library(dplyr)
library(ggplot2)
library(feather)
library(doParallel)
library(arcos)

setwd("~/Documents/arcos/arcos")
registerDoParallel() # registered the parallel backend?
#registerDoParallel(cores=36)
registerDoParallel(cores=18)
batch <- "batch/feather"
feather_files <- list.files(batch)
feather_path <- paste0(batch,  "/", feather_files)
not_pharms <- read_csv("summary_data/not_pharms.csv")

chains <- read_csv("MASTER_pharma_assignment_by_year.csv") %>% 
  filter(!is.na(year)) %>% 
  select(-X1) %>% 
  mutate(year=as.character(year)) %>% 
  select(-year, -method) %>% 
  unique() 


chains_annual <- read_csv("MASTER_pharma_assignment_by_year.csv") %>% 
  filter(!is.na(year)) %>% 
  select(-X1) %>% 
  mutate(year=as.character(year))


### 1. and 2. -----
### Walgreens purchased nearly one out of every five oxycodone and hydrocodone pills
### Walgreens bought 13 billion pills from 2006 - 2012


results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    group_by(BUYER_DEA_NO, BUYER_BUS_ACT) %>% 
    summarize(pils=sum(DOSAGE_UNIT, na.rm=T))
}



results <- results %>% 
  group_by(BUYER_DEA_NO, BUYER_BUS_ACT) %>% 
  summarize(pills=sum(pils, na.rm=T))

results <- left_join(results, chains)

results$buyer_family <- ifelse(is.na(results$buyer_family), "Other", results$buyer_family)

results %>% group_by(buyer_family) %>% 
  summarize(pills=sum(pills)) %>% 
  mutate(percent=round(pills/sum(pills)*100)) 

# I have Walgreens at 18 percent
# Total pills : 12.989 billion

### 3. ----
### Walgreens obtained 97 percent of its pain pills from itself

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    group_by(Reporter_family, BUYER_DEA_NO, BUYER_BUS_ACT) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(Reporter_family, BUYER_DEA_NO, BUYER_BUS_ACT) %>% 
  summarize(pills=sum(pills, na.rm=T))

results <- left_join(results, chains)
results$buyer_family <- ifelse(is.na(results$buyer_family), "Other", results$buyer_family)

reporter_buyer <- results %>% group_by(Reporter_family, buyer_family) %>% 
  summarize(pills=sum(pills)) %>% 
  group_by(buyer_family) %>% 
  mutate(percent=round(pills/sum(pills)*100))

# Walgreen co 97 percent


### 4. ----
### Total pharmacies, around 8,000 in 2012

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    select(BUYER_DEA_NO, BUYER_BUS_ACT, year) %>% 
    unique()
}

results <- unique(results)

results <- left_join(results, chains_annual)
results$buyer_family <- ifelse(is.na(results$buyer_family), "Other", results$buyer_family)

buyers_year <- results %>% count(buyer_family, year)

# 8052 walgreens in 2012

### 5. ----
### Walgreens ordered 30 percent more oxycodone and hydrocodone pills per store on average compared to CVS pharmacies and 85 percent more compared to the rest worldwide

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    select(-mail_hospital) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    group_by(BUYER_DEA_NO, BUYER_BUS_ACT, DRUG_NAME, BUYER_COUNTY, BUYER_STATE, year) %>% 
    summarize(orders=n(), pills=sum(DOSAGE_UNIT, na.rm=T))
}

drug_totals_year <- results %>% 
  group_by(BUYER_DEA_NO, BUYER_BUS_ACT, DRUG_NAME, BUYER_COUNTY, BUYER_STATE, year) %>% 
  summarize(orders=sum(orders), pills=sum(pills, na.rm=T))

drug_totals_year <- left_join(drug_totals_year, chains_annual)

drug_totals_year <- drug_totals_year %>% 
  filter(BUYER_BUS_ACT=="PHARMACY")

drug_totals_year$buyer_family <- ifelse(is.na(drug_totals_year$buyer_family), "Other", drug_totals_year$buyer_family)

drugs <- drug_totals_year %>% 
  group_by(BUYER_DEA_NO, buyer_family, BUYER_COUNTY, BUYER_STATE, year) %>% 
  summarize(pills=sum(pills, na.rm=T)) %>% 
  group_by(buyer_family, BUYER_COUNTY, BUYER_STATE, year) %>% 
  summarize(stores=n(), pills=mean(pills, na.rm=T)) %>% 
  mutate(pills_and_stores=stores*pills) %>% 
  group_by(buyer_family, BUYER_COUNTY, BUYER_STATE) %>% 
  summarize(pills=sum(pills_and_stores), stores=sum(stores)) %>% 
  mutate(avg=pills/stores)

drugs_alt <- drug_totals_year %>% 
  group_by(BUYER_DEA_NO, buyer_family, BUYER_COUNTY, BUYER_STATE, year) %>% 
  summarize(pills=sum(pills, na.rm=T)) %>% 
  group_by(buyer_family, BUYER_COUNTY, BUYER_STATE, year) %>% 
  summarize(stores=n(), pills=mean(pills, na.rm=T)) %>% 
  group_by(buyer_family, BUYER_COUNTY, BUYER_STATE, ) %>% 
  summarize(weighted_avg=weighted.mean(pills, stores))

write_csv(drugs_alt, "family_county_weighted.csv", na="")

pop <- county_population(key="WaPo")

pop <- pop %>% select(BUYER_COUNTY, BUYER_STATE, countyfips) %>% unique()

drugs_alt <- left_join(drugs_alt, pop)

# How much more walgreens than cvs: 30.5521

drug_totals_year$buyer_family <- ifelse(drug_totals_year$buyer_family!="Walgreen Co", "Other", drug_totals_year$buyer_family)
drug_totals_year$buyer_family <- ifelse(is.na(drug_totals_year$buyer_family), "Other", drug_totals_year$buyer_family)

drugs_alt <- drug_totals_year %>% 
  group_by(BUYER_DEA_NO, buyer_family, year) %>% 
  summarize(pills=sum(pills, na.rm=T)) %>% 
  group_by(buyer_family, year) %>% 
  summarize(stores=n(), pills=mean(pills, na.rm=T)) %>% 
  group_by(buyer_family) %>% 
  summarize(weighted_avg=weighted.mean(pills, stores))

# How much more walgreens than everyone else: 72.65606

### 6. ----
### Oviedo store: 30 milligram oxycodone pills doubled from 72,900 in March 2011 to 145,300 pills in July 2011

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(BUYER_DEA_NO=="BW8487438") %>% 
    filter(DRUG_NAME=="OXYCODONE") %>%
    #filter(dos_str==30) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    mutate(month=str_sub(TRANSACTION_DATE, 0,2)) %>% 
    group_by(BUYER_DEA_NO, year, month, dos_str) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(BUYER_DEA_NO, year, month, dos_str) %>% 
  summarize(pills=sum(pills, na.rm=T))

# 73,300 in March 2011 and 145,400 in July 2011

### 7. ----
### Walgreens pharmacy on McHenry Avenue was the single largest purchaser of pain pills in the entire Walgreens chain from 2006 through 2012


results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    #filter(BUYER_DEA_NO=="BW8487438") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    group_by(BUYER_DEA_NO, year) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}


results <- results %>% 
  group_by(BUYER_DEA_NO, year) %>% 
  summarize(pills=sum(pills))

results <- left_join(results, chains_annual)
results$buyer_family <- ifelse(is.na(results$buyer_family), "Other", results$buyer_family)

results_ranked <- results %>% 
  group_by(BUYER_DEA_NO, buyer_family) %>% 
  summarize(pills=sum(pills)) %>% 
  ungroup() %>% 
  mutate(rank=rank(-pills)) %>% 
  arrange(rank)

# 11,908,560 pills, but ranks 44 out of all pharmacies. there are two cvses ahead of it.

### 8. ----
### About one out of every five oxycodone pills ordered at the Modesto pharm was 30 milligrams.


results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(BUYER_DEA_NO=="BW4243426") %>% 
    filter(DRUG_NAME=="OXYCODONE") %>%
    #filter(dos_str==30) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    mutate(month=str_sub(TRANSACTION_DATE, 0,2)) %>% 
    group_by(BUYER_DEA_NO, year, month, dos_str) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(BUYER_DEA_NO, year, month, dos_str) %>% 
  summarize(pills=sum(pills, na.rm=T))

dosages <- results %>% 
  group_by(dos_str) %>% 
  summarize(pills=sum(pills)) %>% 
  mutate(percent=pills/sum(pills)*100)

# okay, BW4243426 is 20 percent, yes

### 9. ----
### Walgreens and four other national chain pharmacies purchased about 1.6 billion of those pills, or roughly one-third of all distributed from 2006 through 2012. 

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE") %>%
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
#    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    #filter(dos_str==30) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    group_by(BUYER_DEA_NO, year, dos_str) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(BUYER_DEA_NO, year, dos_str) %>% 
  summarize(pills=sum(pills, na.rm=T))

results <- left_join(results, chains_annual)
results$buyer_family <- ifelse(is.na(results$buyer_family), "Other", results$buyer_family)

dosages <- results %>% 
  group_by(buyer_family, dos_str) %>% 
  filter(dos_str>=30) %>% 
  group_by(buyer_family) %>% 
  summarize(pills=sum(pills)) %>%
  ungroup() %>% 
  mutate(percent=pills/sum(pills)*100)

results %>% ungroup() %>% summarize(pills=sum(pills))

# 1.6 billion versus 4.9 billion, yup

### 10. ----
### At walgreens, those pills accounted for about 6 percent of the chain's overall opioid business compared to roughly 4.6 percent at CVS and 2 percent at walmart


results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    #filter(DRUG_NAME=="OXYCODONE") %>%
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
    
    #filter(dos_str==30) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    group_by(BUYER_DEA_NO, year, dos_str) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(BUYER_DEA_NO, year, dos_str) %>% 
  summarize(pills=sum(pills, na.rm=T))

results <- left_join(results, chains_annual)
results$buyer_family <- ifelse(is.na(results$buyer_family), "Other", results$buyer_family)


dosages <- results %>% 
  group_by(buyer_family, dos_str) %>% 
  mutate(type=case_when(
    dos_str>=30 ~ "High", 
    TRUE ~ "Low"
  )) %>% 
  group_by(buyer_family, type) %>% 
  summarize(pills=sum(pills)) %>%
  group_by(buyer_family) %>% 
  mutate(percent=round(pills/sum(pills)*100,1))

results %>% ungroup() %>% summarize(pills=sum(pills))

# 6 perent walgreens
# 4.9 at cvs

### 11. ----
###  The Greenville store was the largest buyer of pain pills in the county from 2006 through 2012, and half of the pills ordered were oxycodone-- nearly twice the average of all other pharmacies nationwide


"BW7512595"

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S") %>% 
  #& Measure=="TAB") %>% 
    #filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    #filter(DRUG_NAME=="OXYCODONE") %>%
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
    #filter(dos_str==30) %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    group_by(BUYER_DEA_NO, year, DRUG_NAME) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(BUYER_DEA_NO, year, DRUG_NAME) %>% 
  summarize(pills=sum(pills, na.rm=T))

results2 <- results %>% 
  group_by(BUYER_DEA_NO, DRUG_NAME) %>% 
  summarize(pills=sum(pills)) %>% 
  group_by(BUYER_DEA_NO) %>% 
  mutate(percent=round(pills/sum(pills)*100))

oxy_only <- results2 %>% filter(DRUG_NAME=="OXYCODONE")

oxy_only %>% ungroup() %>% summarize(mean(percent, na.rm=T))
# 29.3 vs 58

### 12. ----
### By the end of 2012, orders of pain pills dipped to 2.2 billion from its peak of 2.4 billion the previous year, analysis shows.

### 13. ----
### But Walgreens was still the largest buyer of pils containing oxycodone and hydrocodone


### 14. ---
### Did BW4243426 have the largest market share of any pharmacy in STANISLAUS county?

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(BUYER_COUNTY=="STANISLAUS" & BUYER_STATE=="CA") %>% 
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    select(-mail_hospital) %>% 
    group_by(BUYER_DEA_NO) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(BUYER_DEA_NO) %>% 
  summarize(pills=sum(pills, na.rm=T))

results2 <- left_join(results, chains)

buyers <- read_csv("buyers_addresses.csv")

## by type

results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(BUYER_COUNTY=="STANISLAUS" & BUYER_STATE=="CA") %>% 
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    #filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    #select(-mail_hospital) %>% 
    group_by(BUYER_DEA_NO, BUYER_BUS_ACT) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

results <- results %>% 
  group_by(BUYER_DEA_NO, BUYER_BUS_ACT) %>% 
  summarize(pills=sum(pills, na.rm=T))

results2 <- left_join(results, chains)


addresses <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(BUYER_COUNTY=="STANISLAUS" & BUYER_STATE=="CA") %>% 
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    left_join(not_pharms) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      !is.na(mail_hospital) ~ mail_hospital,
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    mutate(BUYER_BUS_ACT=case_when(
      BUYER_BUS_ACT=="CHAIN PHARMACY" ~ "PHARMACY",
      BUYER_BUS_ACT=="RETAIL PHARMACY" ~ "PHARMACY",
      TRUE ~ BUYER_BUS_ACT
    )) %>% 
    #filter(BUYER_BUS_ACT=="PHARMACY") %>% 
    #select(-mail_hospital) %>% 
   select(BUYER_DEA_NO, BUYER_BUS_ACT, BUYER_ADDRESS1, BUYER_ADDRESS2, BUYER_ADDL_CO_INFO, BUYER_CITY, BUYER_COUNTY, BUYER_STATE, BUYER_ZIP) %>% 
    unique()
}

addresses <- unique(addresses)
library(arcos)

wpadd <- pharm_latlon(county="STANISLAUS", state="CA", key="WaPo")
stan_hosp <- read_csv("stan_hosp.csv")
stan_hosp$X4 <- NULL
stan_hosp$X7 <- NULL

wpadd <- rbind(wpadd, stan_hosp)
addresses <- left_join(addresses, wpadd)
addresses <- filter(addresses, !is.na(lat))

addresses <- left_join(addresses, results2)
addresses <- addresses %>% 
  mutate(buyer_family=case_when(
    is.na(buyer_family) & BUYER_BUS_ACT!="PHARMACY" ~ "Hospital/Clinic",
    is.na(buyer_family) & BUYER_BUS_ACT=="PHARMACY" ~ "Other",
    TRUE ~ buyer_family
  ))

library(leaflet)

cof <- colorFactor(c("#e41a1c", "#377eb8","#4daf4a","#984ea3","#984ea3"), 
                   domain=c("CVS", "Hospital/Clinic", "Other", "Wal-Mart", "Walgreen Co"))

addresses$text <- paste0("<b>",addresses$buyer_family, "</b><br/>",
                         addresses$BUYER_ADDRESS1, "<br/>",
                         addresses$pills)
m <- leaflet(addresses) %>% 
  addProviderTiles(providers$CartoDB.DarkMatter) %>% 
  setView(-120.981433,37.663025, zoom = 9) %>% 
  addCircleMarkers(~lon, ~lat, popup=addresses$text, weight = 3, radius=log(addresses$pills), 
                   color=~cof(buyer_family), stroke = F, fillOpacity = 0.5) 
m

##
results_summary <- results2 %>% filter(BUYER_DEA_NO!="BK8062197") %>%
  filter(BUYER_BUS_ACT=="PHARMACY") %>% 
  group_by(buyer_family) %>% summarize(pills=sum(pills, na.rm=T))

## OVIEDO CHECK


results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE" | DRUG_NAME=="HYDROCODONE") %>% 
    filter(BUYER_DEA_NO=="BW8487438")
}


# oxy strength




results <- foreach(i=1:length(feather_path), .combine=rbind) %dopar% {
  read_feather(feather_path[i]) %>%
    filter(BUYER_DEA_NO=="BW8487438") %>% 
    filter(TRANSACTION_CODE=="S" & Measure=="TAB") %>% 
    filter(DRUG_NAME=="OXYCODONE") %>% 
    mutate(year=str_sub(TRANSACTION_DATE, -4)) %>% 
    mutate(month=str_sub(TRANSACTION_DATE, 0,2)) %>% 
    group_by(year, month, dos_str) %>% 
    summarize(pills=sum(DOSAGE_UNIT, na.rm=T))
}

library(lubridate)

results <- results %>% 
  group_by(year, month, dos_str) %>% 
  summarize(pills=sum(pills, na.rm=T)) %>% 
  mutate(date=ymd(paste0(year, "/", month, "/01")))

ggplot(results, aes(x=date, y=pills)) + geom_bar(stat="identity") + facet_wrap(~dos_str)

}
